\Title

### 2016-03-20 manuscript/manuscript.tex
Corrections to conclusions by Val (part 1)
Missing the last paragraph

The test on simple synthetic data shows that our inversion method is able to
recover a smooth Moho relief with a homogeneous density-contrast.
The inversion was not able to fully recover the shortest wavelength feature in
the model, possibly due to the smoothness constraints which tends to soften
high-frequency (sharp) variations.
The cross-validation Mean Square Error curve in Fig.~\ref{fig:simple-results}e
has a well-defined minimum, indicating a value of the regularization parameter
($\mu$) whose corresponding estimate best predicts data that were not included
in the inversion.
Using this value of $\mu$ in the inversion leads to a smooth Moho relief and
acceptable data misfit.

The source code profiling results presented in Table~\ref{profiling}
confirm the efficiency of the proposed method.
When using sparse matrices, solving linear systems and performing matrix
multiplications together account for a mere 0.067\% of the total computation
time required for a single inversion.
The majority of the computation time (99.824\%) is spent on forward modeling.
Thus, we are able to retain the high computational efficiency of Bott's method
while using a classic Tikhonov regularization formulation.
This approach could, in theory, be extended to other types of regularization
(e.g., Total Variation) and misfit functions (e.g., re-weighted least squares)
already available in the literature.
For example, the Total Variation approach used by \citet{martins2011} could
potentially be implemented in a more straight forward manner than done by
\citet{santos2015}.

The more complex synthetic data test based on CRUST1.0
(Fig.~\ref{fig:crust1-results})
shows that the cross-validation using pointwise Moho depth information
is able to correctly estimate the density-contrast ($\Delta\rho$) and Normal
Earth Moho depth ($z_{ref}$).
This test indicates that the inversion neither correctly estimates Moho depth
nor adequately fits the gravity and pointwise data when sharp variations in
Moho depth occur.
This phenomenon is particularly strong in the region below the Andes.
A likely explanation is that the smoothness regularization
is intrinsically unable to produce sharp variations in Moho depth.
These effects might be mitigated with the use of sharpness-inducing
regularization, like Total Variation \citep{martins2011},
Cauchy norm regularization \citep{sacchi1996, pilkington2008},
or an adaptive mixed smoothness-sharpness regularization \citep{sun2014}.

@@

We are indebted to the developers and maintainers of the open-source
software without which this work would not have been possible.
L. Uieda was supported by a scholarship from
Coordenação de Aperfeiçoamento de Pessoal de Nível Superior
(CAPES).
V.C.F. Barbosa was supported by a fellowship from
Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq).
\todo{Coloco o projeto da FAPERJ também?}

>>>>

The test on simple synthetic data shows that our inversion method is able to
recover a smooth Moho relief with a homogeneous density-contrast.
The inversion was not able to fully recover the shortest wavelength feature in
the model, possibly due to the smoothness constraints which tends to soften
high-frequency (sharp) variations.
The cross-validation Mean Square Error curve in Fig.~\ref{fig:simple-results}e
has a well-defined minimum, indicating a value of the regularization parameter
($\mu$) whose corresponding estimate best predicts data that were not included
in the inversion.
Using this value of $\mu$ in the inversion leads to a stable solution
characterized by a smooth Moho relief with an acceptable data misfit.

The source code profiling results presented in Table~\ref{profiling}
confirm the efficiency of the proposed method.
When using sparse matrices, solving linear systems and performing matrix
multiplications together account for a mere 0.067\% of the total computation
time required for a single inversion.
The majority of the computation time (99.824\%) is spent on forward modeling.
Thus, we are able to retain the high computational efficiency of Bott's method
and use a classic Tikhonov regularization formulation.
This approach could, in theory, be extended to other types of regularization
(e.g., total variation) and misfit functions (e.g., re-weighted least squares)
already available in the literature.
For example, the total variation approach used by \citet{martins2011} could
potentially be implemented in a more straight forward manner than done by
\citet{santos2015}.

The more complex synthetic data test based on CRUST1.0
(Fig.~\ref{fig:crust1-results})
shows that the cross-validation using pointwise Moho depth information
is able to correctly estimate the density-contrast ($\Delta\rho$) and Normal
Earth Moho depth ($z_{ref}$).
This test indicates that the inversion neither correctly estimates Moho depth
nor adequately fits the gravity and pointwise data when sharp variations in
Moho depth occur.
This phenomenon is particularly strong in the region below the Andes.
A likely explanation is that the smoothness regularization
is intrinsically unable to produce sharp variations in Moho depth.
These effects might be mitigated with the use of sharpness-inducing
regularization, like
the weighted smoothness inversion \citep{barbosa1999a},
Cauchy norm regularization \citep{sacchi1996, pilkington2008},
entropic regularization \citep{silva2010},
total variation regularization \citep{martins2011},
or an adaptive mixed smoothness-sharpness regularization \citep{sun2014}.

@@

We are indebted to the developers and maintainers of the open-source
software without which this work would not have been possible.
L. Uieda was supported by a scholarship from
Coordenação de Aperfeiçoamento de Pessoal de Nível Superior
(CAPES).
V.C.F. Barbosa was supported by a fellowship from
Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq).
